%% start of file 'template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[letterpaper]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
\usepackage{textcomp}
% moderncv themes
\moderncvstyle{classic}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.90]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...
    % Profile
\name{Noah Huber-Feely}{}
\address{70 Morningside Dr.}{New York, NY}
\phone[mobile]{931-636-8567}
\email{nh2567@columbia.edu}
\homepage{github.com/huberf}
    \begin{document}
\makecvtitle
\vspace*{-5mm} % To decrease margin below header block
\section{Education}
\cventry
{Expected 2021}
{BS in Computer Science, Minor in Statistics}
{Columbia University}
{New York, NY}
%{\textit{New York, NY}}
{}
{\begin{itemize}%
%	\item Relevant coursework: Honors Intro to Computer Science (4.0), Honors Data Structures and Algorithms (4.0)
	\item Campus Involvement: Columbia Space Initiative (CubeSat team), Robotics Club, Science Fiction Society
         \item Cumulative GPA: 4.0
	\end{itemize}}
\section{Experience}
\cventry
{Jun 2019 -- Aug 2019}
{Robotics Software Engineering Intern}
{Bear Flag Robotics}
{Sunnyvale, CA}
{}
{\begin{itemize}%
	\item Architected and developed from the ground up their autonomous tractor path generation utility, enabling them to perform their first full farm operation. Managed the paths for all 6 field operations that summer.
	\item Developed an efficient path parametrization and designed fitting algorithms for heuristically optimal coverage and discer performance in any farm field, enabling them to complete the next year of their milestone plan. The tool generates paths 28x faster than their previous utility even while handling arbitrary polygons.
	\item Collaborated on the ROS stack with team of 7 engineers. Concurrently participated in the TEC Fellowship.
	\end{itemize}}
\cventry
{May 2018 -- Aug 2018}
{Software Engineering Intern}
{Chartbeat}
{New York, NY}
{}
{\begin{itemize}%
	\item Worked on every component of the stack (from React to their Python and Redshift back-end). Primarily focused on the back-end and connection to idiomatic React and Angular components.
	\item Enhanced query speeds by up to 80\% through heuristic computation.
	\item Launched their historical analytics product out of beta. Developed majority of new product features and performance improvements. Resulted in all-time highest customer use (210\% higher) of historical analytics.
	\item Advised product vision and built most projects from the front-end design stage to the back-end changes.
	\item Concurrently participated in the HackNY Fellowship, gaining a foundation in the startup world.
	\end{itemize}}
\cventry
{Oct 2016 -- Present}
{Technical Lead}
{LifeTriage}
{Huntsville, AL}
{}
{\begin{itemize}%
	\item Led all current development and independently constructed \& deployed mobile apps for iOS and Android along with a robust web app using React Native, node.js and a MongoDB back-end. (\href{https://ctips.lifetriage.com}{ctips.lifetriage.com})
	\item Improved loading time by over 120\% with WebSockets and developed algorithms for recommendations based on collected user data. Pioneered TensorFlow based career recommendation system.
	\item Directed user testing and analytics, including A/B testing, increasing user engagement 300\%.
	\end{itemize}}
\cventry
{Mar 2016 -- Jul 2017}
{Business Owner}
{Noah's Arc Development}
{Winchester, TN}
{}
{\begin{itemize}%
	\item  Built back-end APIs, mobile apps and websites for 7 clients from small businesses to medium corporations.
	\item  Delegated project tasks and handled small team management. (\href{https://noahcodes.com/}{noahcodes.com})
	\end{itemize}}
\iffalse
\cventry
{May 2015 -- Jun 2017}
{Web Store Admin}
{The Mountain Outfitter's}
{Monteagle, TN}
{}
{\begin{itemize}%
	\item  Executed multiple full site server migrations and data recovery after attempted hack.
	\item  Setup Yii (PHP) based CMS and inventory management system and improved checkout flow.
	\item  Additional payment option integration led to 30\% more transactions.
	\end{itemize}}
\fi
\iffalse
\cventry
{May 2015 -- Sep 2015}
{Computer Science Teacher}
{PEN Foundation}
{Winchester, TN}
{}
{\begin{itemize}%
	\item  Crafted individualized lessons from fundamentals to machine vision for 40 students and built a Wordpress site with lessons for at home learning. Taught K-12 students each Saturday at Winchester Public Library.
	\end{itemize}}
\fi
    \section{Leadership \& Projects}
\cventry
{Jan 2018 - Present}
{Clara Conversational Agent System - Personal}
{}
{\textit{NLP, Weak AI}}
{New York, NY}
{\begin{itemize}%
	\item Engineered a Python PIP package that uses natural language processing techniques to handle small talk queries to chat bot based systems on top of existing frameworks. (github.com/huberf/clara-pip)
\end{itemize}}
\iffalse
\cventry
{Jan 2015 - Present}
{Personal Assistant and Learner (PAL) - Personal}
{}
{\textit{NLP, Weak AI}}
{Winchester, TN}
{\begin{itemize}%
	\item Developed a robust voice and text UI handling both intent parsing as well as execution of "skills" built on the skills framework. Employs TensorFlow to determine context. (github.com/huberf/pal)
\end{itemize}}
\fi
\iffalse
\cventry
{Sep 2015 - Aug 2016}
{Hop Around Huntsville - President}
{}
{\textit{Data Streams, Geospatial}}
{Huntsville, AL}
{\begin{itemize}%
\item Constructed back-end system built for Huntsville, AL government to publicly track their bus network. Employs websockets for real time location delivery. (github.com/codeforhuntsville/transitTracks)
\end{itemize}}
\fi
\iffalse
\cventry
{Sep 2016 - Present}
{Quantified Self - Personal}
{}
{\textit{Data Collection, Prediction and Inference}}
{New York, NY}
{\begin{itemize}%
\item Collected millions of data points (e.g. heart rate variability, coffee intake, task
completion rate) and write systems to analyze and offer suggestions to improve myself. Employed TensorFlow models to derive correlations.
\end{itemize}}
\fi
\cventry
{Jun 2018 - Mar 2019}
{Head Parsing Engineer - Iran Data Mining}
{}
{\textit{Columbia Journalism School}}
{New York, NY}
{\begin{itemize}%
	\item Engineered NLP parsing algorithms and a multithreaded fault tolerant data pipeline to mine 1,332,236 Farsi documents from the Iranian government's collection of official business statements. The cleaned data is currently being used by a Columbia Journalism team to find corruption and sanction violations within the Iranian elite.
\end{itemize}}
%\vspace{1mm}
    
\ 
\section{Skills}
\cvitem{Languages}{Python, R, Javascript, C++, Java, Scala (intermediate), HTML, LaTeX, SQL, CSS}
\cvitem{Frameworks}{React Native, Node.js, Express.js, Socket.io, ROS, React, Angular, TensorFlow, ElasticSearch}
\cvitem{Utilities}{Git, Kafka, Bash, MongoDB, Redis, PostgreSQL, AWS S3, Xcode, Android Studio, Docker}
%\cvitem{Passions}{Running, Quantified Self, Science Fiction}

\end{document}
